FoRTE baseline

### 2019-09-10 analysis/paper/paper.Rmd
Save figure files as PNG
This makes building the manuscript _much_ faster

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>"
  ## fig.path = "../figures/"
)

@@

```{r param_dist, fig.cap = param_dist_cap, fig.dim = c(13, 10)}
readd(param_dist_gg)
```

@@

```{r summary-ts-plot, fig.cap = summary_ts_cap, fig.dim = c(10, 10)}
summary_ts_cap <- paste(
  htmlfig(),
  "ED2 plot-level predictions of",
  "gross (GPP) and net (NPP) primary productivity,",
  "aboveground biomass (AGB),",
  "total leaf area index (LAI),",
  "and Shannon diversity index (of plant functional types)",
  "by model configuration.",
  "The solid line is the ensemble mean.",
  "The dashed line is the 80% confidence interval.",
  "Black dot with error bars is the mean and min/max value",
  "from Hardiman et al. (2013)."
)
readd(summary_ts_plot)
```

@@

```{r pairs-time, fig.cap = pairs_time_cap, fig.dim = c(8, 8)}
pairs_time_cap <- paste(
  htmlfig(),
  "Post-1975 growing season averaged NPP vs. LAI, with observation (in black)",
  "and linear regression, by model type.",
  "Letter labels are selected runs with the same parameters,",
  "and match the rows in Figure 4."
)
readd(pairs_time_averaged)
```

In most simulations, the leaf area index was too low for a given level of net primary productivity, but the relationship between these two variables varied with model configuration (Figure 3).
The crown model (closed vs. finite) had the strongest effect:
Compared to the simulations with "closed" crowns, simulations with finite canopy radius generally had lower net primary productivity for the same leaf area index.
Only a few individual simulations matched _both_ the observed leaf area index and net primary productivity, and all of them had the finite canopy radius configuration.

```{r bigfacet-plot, fig.cap = bigfacet_cap, fig.dim = c(12, 8)}
bigfacet_cap <- paste(
  htmlfig(),
  "PFT-level predictions of leaf area index (LAI) by model configuration and parameterization.",
  "Each row of plots is a simulation with the same set of parameters across model configurations.",
  "Letters correspond to the labels in Figure 3.",
  "Note that these are predictions of total leaf area index summed across all cohorts of the same PFT,",
  "meaning that higher LAI in one PFT does not necessarily indicate dominance, size, etc."
)
readd(lai_pft_plot)
```

@@

```{r within-vs-across, fig.cap = within_vs_across_cap, fig.dim = c(9, 4)}
within_vs_across_cap <- paste(
  htmlfig(),
  "Comparison of parametric uncertainty within ensembles (colored bars, colored by model type)",
  "and \"structural\" uncertainty (variance in ensemble means; black bar) by output variable.",
  "Output variables are expressed as growing season averages for all years after 1910."
)
readd(within_across_plot)
```

@@

```{r uncertainty-analysis, fig.cap = uncertainty_analysis_cap, fig.dim = c(20, 15)}
uncertainty_analysis_cap <- paste(
  htmlfig(),
  "PEcAn-like parameter sensitivity and uncertainty analysis, by model type,",
  "for 1975-2000 averaged growing season net primary productivity (left) and leaf area index (right).",
  "Elasticity (top) is the normalized sensitivity of the model to a fixed change in the parameter.",
  "Partial variance (bottom) describes the overall contribution of the parameter to model predictive uncertainty based on the combination of parameter uncertainty and model sensitivity.",
  "Each panel shows the top 10 parameter values, in terms of the absolute value of the corresponding quantity.",
  "Input parameter distributions are shown in Figure 1.",
  "Note that x-axis scales vary across panels."
)
readd(sensitivity_plot)
```

>>>>

```{r, setup, echo = FALSE}
library(knitr)
library(here)
library(drake)

fig <- function(...) {
  filepath <- here("analysis", "figures", ...)
  knitr::include_graphics(file_in(filepath))
}

opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>"
  ## fig.path = "../figures/"
)

@@

```{r param_dist, fig.cap = param_dist_cap}
fig("param-dist.png")
```

@@

```{r summary-ts-plot, fig.cap = summary_ts_cap}
summary_ts_cap <- paste(
  htmlfig(),
  "ED2 plot-level predictions of",
  "gross (GPP) and net (NPP) primary productivity,",
  "aboveground biomass (AGB),",
  "total leaf area index (LAI),",
  "and Shannon diversity index (of plant functional types)",
  "by model configuration.",
  "The solid line is the ensemble mean.",
  "The dashed line is the 80% confidence interval.",
  "Black dot with error bars is the observed mean and min/max value",
  "(TODO REF)."
)
fig("summary-ts-plot.png")
```

@@

```{r pairs-time, fig.cap = pairs_time_cap}
pairs_time_cap <- paste(
  htmlfig(),
  "Post-1975 growing season averaged NPP vs. LAI, with observation (in black)",
  "and linear regression, by model type.",
  "Letter labels are selected runs with the same parameters,",
  "and match the rows in Figure 4."
)
fig("pairs-time-averaged.png")
```

The crown model (closed vs. finite) had the strongest effect:
Compared to the simulations with "closed" crowns, simulations with finite canopy radius generally had lower net primary productivity for the same leaf area index.
Only a few individual simulations matched _both_ the observed leaf area index and net primary productivity, and all of them had the finite canopy radius configuration.

```{r bigfacet-plot, fig.cap = bigfacet_cap}
bigfacet_cap <- paste(
  htmlfig(),
  "PFT-level predictions of leaf area index (LAI) by model configuration and parameterization.",
  "Each row of plots is a simulation with the same set of parameters across model configurations.",
  "Letters correspond to the labels in Figure 3.",
  "Note that these are predictions of total leaf area index summed across all cohorts of the same PFT,",
  "meaning that higher LAI in one PFT does not necessarily indicate dominance, size, etc."
)
fig("lai-pft-plot.png")
```

@@

```{r within-vs-across, fig.cap = within_vs_across_cap, fig.dim = c(9, 4)}
within_vs_across_cap <- paste(
  htmlfig(),
  "Comparison of parametric uncertainty within ensembles (colored bars, colored by model type)",
  "and \"structural\" uncertainty (variance in ensemble means; black bar) by output variable.",
  "Output variables are expressed as growing season averages for all years after 1910."
)
fig("within-across-plot.png")
```

@@

```{r uncertainty-analysis, fig.cap = uncertainty_analysis_cap}
uncertainty_analysis_cap <- paste(
  htmlfig(),
  "PEcAn-like parameter sensitivity and uncertainty analysis, by model type,",
  "for 1975-2000 averaged growing season net primary productivity (left) and leaf area index (right).",
  "Elasticity (top) is the normalized sensitivity of the model to a fixed change in the parameter.",
  "Partial variance (bottom) describes the overall contribution of the parameter to model predictive uncertainty based on the combination of parameter uncertainty and model sensitivity.",
  "Each panel shows the top 10 parameter values, in terms of the absolute value of the corresponding quantity.",
  "Input parameter distributions are shown in Figure 1.",
  "Note that x-axis scales vary across panels."
)
fig("sensitivity-plot.png")
```
